On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-07 main.tex
Update main.tex
Corrections in Section 5

\section{Bit complexity}%

@@

For a matrix $A \in \GL(n,\Q),$ let 
Y_i = X_i^{A} = [b_i] \cdot \bbm X_1\\ \vdots \\ X_n \ebm, 
where $b_i$ is the i-th row of $A^{-1}$.

@@

\KwIn{a strait line program $\Gamma$ that computes $f \in \Q[X_1,\hdots,X_n],$ and $d=\deg(f)$}

@@

\nl Take $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $A \in S^{n^2}$, and  $\sigma \in T^{n-1}$\;
\nl Apply the change of variables to obtain $f(A x)=f^A(x)$\;
\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}$\;

@@

$\{Y_1-\sigma_1,\hdots,Y_{i-1}-\sigma_{i-1},f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n} \}$\;

@@

@@

    \item  We can prepare a straight-line program $\Gamma$ for $f^A$ with length at most $d^n$, and 
    by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, height of at most 

@@

\textbf{Probability of success:} Let $\Delta_i \in \C[\A]$ be the polynomials from Theorem 2.1. Denote by $\Delta$ the product $\Delta := \prod_{i=1}^n \D_i.$ Note that 

@@

where then, if $\mA \in \C^{n \times n}$ does not cancel $\Delta,$ then  $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for all $i \in \{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let $\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 and denote by $\Xi$ the product $\Xi := \prod_{i=1}^n \Xi_i.$ Note that 

@@

where then, if $\sigma \in \C^{i-1}$ does not cancel $\Xi$ then $f^{\mA}$ and $\sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ 
Now, by construction of \[S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}\] and \[T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},\] where $A \in S^{n^2}$ and  $\sigma \in T^{n-1}$ are randomly chosen, we have 

@@

\pr[A \in \Delta] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3

@@

\pr[\sigma \in \Xi] \leq \deg \frac{\deg\Xi}{|S|} = \epsilon/3.

@@

 \pr[A \not\in \Delta] \times \pr[\sigma \not \in \Xi ~|~A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi].

@@

Set $k = \lg(3n/\epsilon)$, with $\epsilon>0,$ so that 

@@

\pr[\textrm{success}] &\geq  (1- \epsilon/3)(1- \epsilon/3)\pr[\mathscr{E}~|~A \not\in \Delta \textrm{ and } \sigma \not \in \Xi]\\

>>>>

\section{Bit complexity}

@@

The following is our main algorithm. In step 5, we use  \cite[Algorithm 2]{SH} to solve a square system. This subroutine is randomized. In order to guarantee a higher probability of success, we repeat the calculation $k$ times. This subroutine also requires a straight-line program as input, which we compute from $f^\mA$ and its partial derivatives. 

@@

\KwIn{$f \in \Q[X_1,\hdots,X_n]$ of degree $d$ and $0 < \epsilon < 1$}

@@

\nl Construct $S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}$ and $T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},$ and randomly choose $\mA \in S^{n^2}$, and  $\bm \sigma \in T^{n-1}$\;
\nl Apply the change of variables to obtain $f(\mA x)=f^{\mA}(x)$\;
\nl Use \cite{partialDerComputation} to compute the partial derivatives $\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n}$\;

@@

$\{X_1-\sigma_1,\hdots,X_{i-1}-\sigma_{i-1},f^{\mA},\frac{\pa f^{\mA}}{\pa X_{i+1}},\hdots,\frac{\pa f^{\mA}}{\pa X_n} \}$\;

@@

\clearpage 

@@

    \item  We can prepare a straight-line program $\Gamma$ for $f^{\mA}$ with length at most $d^n$, and 
    by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, height at most 

@@

\textbf{Probability of success:} Let $\Delta_i \in \C[\A]$ be the polynomials from Theorem 2.1. Denote by $\Delta := \prod_{i=1}^n \D_i,$ and note that 

@@

where then, if $\mA \in \C^{n \times n}$ does not cancel $\Delta,$ then  $\mA$ is invertible and $f^\mA$ satisfies $\textbf{H}_i$ for all $i \in \{1,\hdots,n\}.$ Now, assuming that $\mA$ is such a matrix, let $\Xi_i\in \C[\A]$ be the polynomials from Theorem 2.2 applied to $f^{\mA}.$ Denote by $\Xi := \prod_{i=1}^n \Xi_i,$ and note that 

@@

where then, if $\bm \sigma \in \C^{i-1}$ does not cancel $\Xi$ then $f^{\mA}$ and $\bm \sigma$ satisfy $\textbf{H}_i^{'}$ for all $i \in \{1,\hdots,n\}.$ 
Now, by construction of 

@@

S := \{1,2,\hdots,3\epsilon^{-1}6n^3(2d)^{2n}\}

@@

T := \{1,2,\hdots,3\epsilon^{-1}nd^{2n}\},
where $\mA \in S^{n^2}$ and  $\bm \sigma \in T^{n-1}$ are randomly chosen, we have 
\pr[\mA \in \Delta] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
\pr[\bm \sigma \in \Xi] \leq \deg \frac{\deg\Xi}{|S|} = \epsilon/3.

@@

 \pr[\mA \not\in \Delta] \times \pr[\bm \sigma \not \in \Xi ~|~\mA \not\in \Delta] \times \pr[\mathscr{E}~|~\mA \not\in \Delta \textrm{ and } \bm\sigma \not \in \Xi].

@@

Set $k = \lg(3n/\epsilon)$ so that 

@@

\pr[\textrm{success}] &\geq  (1- \epsilon/3)(1- \epsilon/3)\pr[\mathscr{E}~|~\mA \not\in \Delta \textrm{ and } \bm \sigma \not \in \Xi]\\
